A pipeline to analyse time-course gene expression data

### 2019-10-02 manuscript.tex
Deploy NelleV/2019timecourse-rnaseq-pipeline to github.com/NelleV/2019timecourse-rnaseq-pipeline.git:gh-pages

\textbf{EAP: It seems like a problem to have the colors defined in a utils.R. Makes it hard It's not echo'd by markdown and so readers won't know where they come from. (I didn't).}

@@

\emph{EAP}: I moved this here, because we use meta a lot in the eda.

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-8-1} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-26-1} \end{center}

@@

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-31-1} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-36-1} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-36-2} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-38-1} \end{center}

@@

>>>>

@@

Before we dive into the exploratory analysis and quality control, let us
define color schemes for our data that we will use across the whole analysis.
We define coloschemes for groups, timepoints as named vectors.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{group_colors =}\StringTok{ }\KeywordTok{c}\NormalTok{(}
    \StringTok{"M"}\NormalTok{=}\StringTok{"dodgerblue4"}\NormalTok{,}
    \StringTok{"K"}\NormalTok{=}\StringTok{"gold"}\NormalTok{,}
    \StringTok{"C"}\NormalTok{=}\StringTok{"orange"}\NormalTok{,}
    \StringTok{"VH"}\NormalTok{=}\StringTok{"red4"}\NormalTok{,}
    \StringTok{"VL"}\NormalTok{=}\StringTok{"red2"}\NormalTok{)}
\NormalTok{time_colors =}\StringTok{ }\NormalTok{grDevices}\OperatorTok{::}\KeywordTok{rainbow}\NormalTok{(}\DecValTok{15}\NormalTok{)[}\DecValTok{1}\OperatorTok{:}\DecValTok{14}\NormalTok{]}
\KeywordTok{names}\NormalTok{(time_colors) =}\StringTok{ }\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{3}\NormalTok{, }\DecValTok{6}\NormalTok{, }\DecValTok{9}\NormalTok{, }\DecValTok{12}\NormalTok{, }\DecValTok{18}\NormalTok{, }\DecValTok{24}\NormalTok{, }\DecValTok{30}\NormalTok{, }\DecValTok{36}\NormalTok{, }\DecValTok{48}\NormalTok{, }\DecValTok{60}\NormalTok{, }\DecValTok{72}\NormalTok{, }\DecValTok{120}\NormalTok{, }\DecValTok{168}\NormalTok{)}

\CommentTok{# Combine all color schemes into one named lists.}
\NormalTok{ann_colors =}\StringTok{ }\KeywordTok{list}\NormalTok{(}
    \DataTypeTok{Timepoint=}\NormalTok{time_colors,}
    \DataTypeTok{Group=}\NormalTok{group_colors}
\NormalTok{    )}

\NormalTok{replicate_markers =}\StringTok{ }\KeywordTok{c}\NormalTok{(}\DecValTok{15}\NormalTok{, }\DecValTok{17}\NormalTok{, }\DecValTok{19}\NormalTok{)}
\KeywordTok{names}\NormalTok{(replicate_markers) =}\StringTok{ }\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{, }\DecValTok{3}\NormalTok{)}
\NormalTok{ann_markers =}\StringTok{ }\KeywordTok{list}\NormalTok{(}
    \DataTypeTok{Replicate=}\NormalTok{replicate_markers)}
\end{Highlighting}
\end{Shaded}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-9-1} \end{center}

@@

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-29-1} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-32-1} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-37-1} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-37-2} \end{center}

@@

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-40-1} \end{center}
